### 2025-02-09 data-visualization.qmd
20250208 - figure caption

```{r}
ggExtra::ggMarginal(
  plot_ypcByPlayerAge,
  type = "densigram")
```

>>>>

We can also add a marginal density/histogram, as in @fig-scatterplot12:

```{r}
#| label: fig-scatterplot12
#| fig-cap: "Scatterplot With Marginal Density/Histogram."
#| fig-alt: "Scatterplot With Marginal Density/Histogram."

ggExtra::ggMarginal(
  plot_ypcByPlayerAge,
  type = "densigram")
```
